---
title: "Social Network Analysis"
author: "MEENOWA Sarvesh"
date: "02/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


```{r}
## Load important libraries
library(igraph)
library(readr)
library(dplyr)
library(networkD3)
library(gganimate)
#library(gapminder)
library(ggplot2)
library(tidyverse)
library(circlize)
library(ggraph)
library(tidygraph)
library(corrr)
library(RColorBrewer)

```


```{r}
#import dataframe
df <- read_csv("H:/Downloads/Datatsets/Auditions.db.comp (1).csv", locale = locale(encoding = "ISO-8859-1"))
head(df)
```

## Simple SNA


Create a subset of the dataset and represent a bipartite and a multipartite graph 
of internal members, and the same thing external members (do not mix years) :
1. 2017, internal members
2. 2017, external members
3. 2018, internal members
4. 2018, external members
5. 2019, internal members
6. 2019, external members
7. 2020, internal members
8. 2020, external members

```{r}
#2017 internal members
interne_2017 = df %>% filter(status == 'interne' & year == 2017)
#2017 external members
externe_2017 = df %>% filter(status == 'externe' & year == 2017)
#2018 internal members
interne_2018 = df %>% filter(status == 'interne' & year == 2018)
#2018 external members
externe_2018 = df %>% filter(status == 'externe' & year == 2018)
#2019 internal members
interne_2019 = df %>% filter(status == 'interne' & year == 2019)
#2019 external members
externe_2019 = df %>% filter(status == 'externe' & year == 2019)
#2020 internal members
interne_2020 = df %>% filter(status == 'interne' & year == 2020)
#2020 external members
externe_2020 = df %>% filter(status == 'externe' & year == 2020)
```



Use gganimate (in R, or any Python equivalent) to create a GIF-based succession of graphs for the years 2017 to 2020, for external members only(GGanimate doesn't work on networks)
. Make an interactive graph of one year (internal members) with networkD3 (or the
Python equivalent).

```{r}
#create edgelist for every dataset
#extern 2017
externe_2017_edge_list_name <- externe_2017 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(externe_2017_edge_list_name)

#create node list

#  Get distinct source names
sources1 <-externe_2017_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations1 <- externe_2017_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes1 <- inner_join(sources1, destinations1, by = "label") 
nodes1 <- nodes1 %>%
  mutate(id = 1:nrow(nodes1)) %>%
  select(id, everything())
head(nodes1, 3)

# Rename the n.call column to weight
 externe_2017_edge_list_name <- externe_2017_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges1 <-externe_2017_edge_list_name  %>% 
  left_join(nodes1, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges1 <- edges1 %>% 
  left_join(nodes1, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges1 <- select(edges1, from, to, weight)
head(edges1, 3)
```






```{r}
set.seed(4)
net.tidy1 <- tbl_graph(
  nodes = nodes1, edges = edges1, directed = TRUE
  )
ggraph(net.tidy1, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```




```{r}
#interne 2017
interne_2017_edge_list_name <- interne_2017 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(interne_2017_edge_list_name)

#create node list

#  Get distinct source names
sources2 <-interne_2017_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations2 <- interne_2017_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes2 <- inner_join(sources2, destinations2, by = "label") 
nodes2 <- nodes2 %>%
  mutate(id = 1:nrow(nodes2)) %>%
  select(id, everything())
head(nodes2, 3)

# Rename the n.call column to weight
 interne_2017_edge_list_name <- interne_2017_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges2 <-interne_2017_edge_list_name  %>% 
  left_join(nodes2, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges2 <- edges2 %>% 
  left_join(nodes2, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges2 <- select(edges2, from, to, weight)
head(edges2, 3)
```

```{r}
set.seed(12)
net.tidy2 <- tbl_graph(
  nodes = nodes2, edges = edges2, directed = TRUE
  )
ggraph(net.tidy2, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```
```{r}
#externe 2018
externe_2018_edge_list_name <- externe_2018 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(externe_2018_edge_list_name)

#create node list

#  Get distinct source names
sources3 <-externe_2018_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations3 <- externe_2018_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes3 <- inner_join(sources3, destinations3, by = "label") 
nodes3 <- nodes3 %>%
  mutate(id = 1:nrow(nodes3)) %>%
  select(id, everything())
head(nodes3, 3)

# Rename the n.call column to weight
 externe_2018_edge_list_name <- externe_2018_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges3 <-externe_2018_edge_list_name  %>% 
  left_join(nodes3, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges3 <- edges3 %>% 
  left_join(nodes3, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges3 <- select(edges3, from, to, weight)
head(edges3, 3)
```
```{r}
set.seed(123)
net.tidy3 <- tbl_graph(
  nodes = nodes3, edges = edges3, directed = TRUE
  )
ggraph(net.tidy3, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```


```{r}
#interne 2018
interne_2018_edge_list_name <- interne_2018 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(interne_2018_edge_list_name)

#create node list

#  Get distinct source names
sources4 <-interne_2018_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations4 <- interne_2018_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes4 <- inner_join(sources4, destinations4, by = "label") 
nodes4 <- nodes4 %>%
  mutate(id = 1:nrow(nodes4)) %>%
  select(id, everything())
head(nodes4, 3)

# Rename the n.call column to weight
 interne_2018_edge_list_name <- interne_2018_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges4 <-interne_2018_edge_list_name  %>% 
  left_join(nodes4, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges4 <- edges4 %>% 
  left_join(nodes4, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges4 <- select(edges4, from, to, weight)
head(edges4, 3)

```

```{r}
set.seed(154)
net.tidy4 <- tbl_graph(
  nodes = nodes4, edges = edges4, directed = TRUE
  )
ggraph(net.tidy4, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()

```
```{r}
#interne 2019
interne_2019_edge_list_name <- interne_2019 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(interne_2019_edge_list_name)

#create node list

#  Get distinct source names
sources5 <-interne_2019_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations5 <- interne_2019_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes5 <- inner_join(sources5, destinations5, by = "label") 
nodes5 <- nodes5 %>%
  mutate(id = 1:nrow(nodes5)) %>%
  select(id, everything())
head(nodes5, 3)

# Rename the n.call column to weight
 interne_2019_edge_list_name <- interne_2019_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges5 <-interne_2019_edge_list_name  %>% 
  left_join(nodes5, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges5 <- edges5 %>% 
  left_join(nodes5, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges5 <- select(edges5, from, to, weight)
head(edges5, 3)
```
```{r}
set.seed(154)
net.tidy5 <- tbl_graph(
  nodes = nodes5, edges = edges5, directed = TRUE
  )
ggraph(net.tidy5, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```
```{r}
#externe 2019
externe_2019_edge_list_name <- externe_2019 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(externe_2019_edge_list_name)

#create node list

#  Get distinct source names
sources6 <-externe_2019_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations6 <- externe_2019_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes6 <- inner_join(sources6, destinations6, by = "label") 
nodes6 <- nodes6 %>%
  mutate(id = 1:nrow(nodes6)) %>%
  select(id, everything())
head(nodes6, 3)

# Rename the n.call column to weight
 externe_2019_edge_list_name <- externe_2019_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges6 <-externe_2019_edge_list_name  %>% 
  left_join(nodes6, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges6 <- edges6 %>% 
  left_join(nodes6, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges6 <- select(edges6, from, to, weight)
head(edges6, 3)

```
```{r}
set.seed(154)
net.tidy6 <- tbl_graph(
  nodes = nodes6, edges = edges6, directed = TRUE
  )
ggraph(net.tidy6, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```

```{r}
#externe 2020
externe_2020_edge_list_name <- externe_2020 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(externe_2020_edge_list_name)

#create node list

#  Get distinct source names
sources7<-externe_2020_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations7 <- externe_2020_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes7<- inner_join(sources7, destinations7, by = "label") 
nodes7 <- nodes7 %>%
  mutate(id = 1:nrow(nodes7)) %>%
  select(id, everything())
head(nodes7, 3)

# Rename the n.call column to weight
 externe_2020_edge_list_name <- externe_2020_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges7 <-externe_2020_edge_list_name  %>% 
  left_join(nodes7, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges7 <- edges7 %>% 
  left_join(nodes7, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges7 <- select(edges7, from, to, weight)
head(edges7, 3)
```
```{r}
set.seed(123)
net.tidy7 <- tbl_graph(
  nodes = nodes7, edges = edges7, directed = TRUE
  )
ggraph(net.tidy7, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```
```{r}
#interne 2020
interne_2020_edge_list_name <- interne_2020 %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(interne_2020_edge_list_name)

#create node list

#  Get distinct source names
sources8 <-interne_2020_edge_list_name  %>% distinct(Name1) %>% rename(label = Name1)
# Get distinct destination names
destinations8 <- interne_2020_edge_list_name %>%
  distinct(Name2) %>%
  rename(label = Name2)
# Join the two data to create node
# Add unique ID for each country
nodes8<- inner_join(sources8, destinations8, by = "label") 
nodes8 <- nodes8 %>%
  mutate(id = 1:nrow(nodes8)) %>%
  select(id, everything())
head(nodes8, 3)

# Rename the n.call column to weight
 interne_2020_edge_list_name <- interne_2020_edge_list_name %>%
  rename(weight = n_poste)
## (a) Join nodes id for source column
edges8 <-interne_2020_edge_list_name  %>% 
  left_join(nodes8, by = c("Name1" = "label")) %>% 
  rename(from = id)
# (b) Join nodes id for destination column
edges8 <- edges8 %>% 
  left_join(nodes8, by = c("Name2" = "label")) %>% 
  rename(to = id)
# (c) Select/keep only the columns from and to
edges8 <- select(edges8, from, to, weight)
head(edges8, 3)
```
```{r}
set.seed(123)
net.tidy8 <- tbl_graph(
  nodes = nodes8, edges = edges8, directed = TRUE
  )
ggraph(net.tidy8, layout = "graphopt") + 
  geom_edge_link(width = 0.5, colour = "lightgray") +
  geom_node_point(size = 1.5, colour = "#00AFBB") +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```

Make an interactive graph of one year (internal members) with networkD3.

```{r}
#subset interne 2017 to select n_poste and ID
interne_2017_2 = interne_2017 %>% select(n_poste, ID)
head(interne_2017_2)
```


```{r}
#create igraph ibject
graph_interne_2017 <- graph_from_data_frame(interne_2017_2, directed = FALSE)
V(graph_interne_2017)$label <- V(graph_interne_2017)$name
```

```{r}
# Use igraph to make the graph and find membership
wc <- cluster_walktrap(graph_interne_2017)
members <- membership(wc)
#create graph object for network D3
graph_interne_2017_d3 <- igraph_to_networkD3(graph_interne_2017, group = members)
#head(graph_interne_2017_d3)
```
```{r}
# Create force directed network plot
forceNetwork(
Links = graph_interne_2017_d3$links,
Nodes = graph_interne_2017_d3$nodes,
Source = 'source',
Target = 'target',
NodeID = 'name',
Group = 'group'
)
```




Plot a network graph where the vertices are colored by levels of the juries(additional i.e not in documentation)

```{r}
#filter for 2017
interne_2017 = df %>% filter(status == 'interne' & year == 2017)
externe_2017 = df %>% filter(status == 'externe' & year == 2017)
#recode ?MCF to MCF and PUPH to PU-PH
externe_2017$Level[externe_2017$Level == "?MCF"]  <- "MCF"
externe_2017$Level[externe_2017$Level == "PUPH"]  <- "PU-PH"
interne_2017$Level[interne_2017$Level == "?MCF"]  <- "MCF"
interne_2017$Level[interne_2017$Level == "PUPH"]  <- "PU-PH"

```

Checking for external 2017 and coloring by level

```{r}
#self join to create edge list for external 2017
externe_2017_edge_list_name <- externe_2017 %>% select(Level, n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(externe_2017_edge_list_name)
```



```{r}
externe_2017_matrix_name <- as.matrix(externe_2017_edge_list_name[c('Name1', 'Name2')]) 
```


```{r}
set.seed(123)


externe_2017$Level <- as.factor(externe_2017$Level)
#generate palette of 10 colours

pal <- brewer.pal(n = 10, name = 'Paired')

vertex.col <- pal[(externe_2017$Level)]


#plot external 2017 graph colored by level of jury
graph_externe_2017 <- graph_from_edgelist(externe_2017_matrix_name, directed = FALSE)



plot(graph_externe_2017,
     vertex.label = NA, vertex.size = 8, vertex.color = vertex.col)

legend("topleft",bty = "n",
       legend=levels((externe_2017$Level)),
       fill=pal, border=NA)


```

Color by institutions
```{r}
#check how many institutions there are
length(unique(externe_2017$institutions))
```

```{r}
#self join to create external graph but this time with institutions
externe_2017_edge_list_name <- externe_2017 %>% select(institutions, n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(externe_2017_edge_list_name)
```



```{r}
externe_2017_matrix_name <- as.matrix(externe_2017_edge_list_name[c('Name1', 'Name2')]) 
```


```{r}
set.seed(123)


externe_2017$institutions <- as.factor(externe_2017$institutions)
#generate palette of colors
pal = grDevices::colors()[grep('gr(a|e)y', grDevices::colors(), invert = T)]

#pal <- brewer.pal(n = 10, name = 'Paired')
vertex.col <- pal[(externe_2017$institutions)]



graph_externe_2017 <- graph_from_edgelist(externe_2017_matrix_name, directed = FALSE)

#plot external jury members for 2017 colored by institutions

plot(graph_externe_2017,
     vertex.label = NA, vertex.size = 8, vertex.color = vertex.col)

legend("topleft",bty = "n",
       legend=levels((externe_2017$institutions)),
       fill=pal, border=NA,cex=0.5)


```
- A lot of links >> since juries travel/move from different institutions to select candidates

```{r}
set.seed(123)
pal <- brewer.pal(n = 10, name = 'Paired')
interne_2017$Level <- as.factor(interne_2017$Level)


#internal 2017 colored by level
vertex.col <- pal[(interne_2017$Level)]

plot(graph_interne_2017,
     vertex.label = NA, vertex.size = 8, vertex.color = vertex.col)

legend("topleft",bty = "n",
       legend=levels(interne_2017$Level),
       fill=pal, border=NA,cex=1)


```
- Some networks are uncolored because the rows have N/A as institutions
- Each small network represent an institution or institutions with their partners
-(From the figure colored by level), we can see that in each small network there is atleast one PR(Professeurs des universités),each small network represent an institution and if there are multiple PR , it could be different departments of an institution or partner institutions


```{r}
pal <- brewer.pal(n = 10, name = 'Paired')

interne_2017$institutions <- as.factor(interne_2017$institutions)

# interne_2017$Level[interne_2017$Level == "?MCF"]  <- "MCF"
# interne_2017$Level[interne_2017$Level == "PUPH"]  <- "PU-PH"

#internal 2017 colored by institutions

vertex.col <- pal[(interne_2017$institutions)]

plot(graph_interne_2017,
     vertex.label = NA, vertex.size = 8, vertex.color = vertex.col)

legend("topleft",bty = "n",
       legend=levels(interne_2017$institutions),
       fill=pal, border=NA)
```






Apply a community detection approach to detect communities in one of the graphs with only external members
```{r}
# Community Detection ----------------------------------------------------
# Louvain
#apply community detection on external members 2017
lc_externe_2017 <- cluster_louvain(graph_externe_2017)
# membership(lc_externe_2017)
# communities(lc_externe_2017)
plot(lc_externe_2017, graph_externe_2017, vertex.label = NA, vertex.size = 7)
```
```{r}
#infomap method - community detection
imc_externe_2017 <- cluster_infomap(graph_externe_2017)

plot(imc_externe_2017, graph_externe_2017, vertex.label = NA, vertex.size = 8)
```

Create a last graph where all years are pooled together, but only for external
members. What is the problem with this graph ?

```{r}
#filter df for externe only
externe = df %>% filter(status == "externe")
#self join for externe
externe_edge_list_name <- externe %>% select(n_poste, Name) %>%
  inner_join(., select(., n_poste, Name), by = "n_poste") %>%
  rename(Name1 = Name.x, Name2 = Name.y) %>%
  filter(Name1 != Name2) %>%
  unique %>%
  arrange(n_poste)

head(externe_edge_list_name)

```



```{r}
#create matrix from dataframe
externe_matrix_name <- as.matrix(externe_edge_list_name[c('Name1', 'Name2')]) 
#color by level
externe$Level <- as.factor(externe$Level)
graph_externe <- graph_from_edgelist(externe_matrix_name, directed = FALSE)
plot(graph_externe, vertex.label = NA, vertex.size = 8, vertex.color = externe$Level)


```

## Centrality measures
Choose the relevant dataset to compute the following indicators. Identify
the top ten members (create a table per indicator) with the highest values for
the following indicators : degree, strength, betweenness.(https://dshizuka.github.io/networkanalysis/04_measuring.html)
https://medium.com/@615162020004/social-network-analysis-with-r-centrality-measure-86d7fa273574

Create the plots but 
this time, the width of the nodes should depend upon the value of the centrality
indicators.


```{r}
#create sub dataframe for external 2017
externe_2017_2 = externe_2017 %>% select(n_poste, Name)
head(externe_2017_2)
```



```{r}
#get adjacency matrix from edge list 
graph_2017_ex <- graph_from_edgelist(as.matrix(externe_2017_edge_list_name[c("Name1","Name2")]), directed = FALSE)
```


```{r}
#show igraph object
graph_2017_ex
```

```{r}
#graph - node size depends on degree centrality
set.seed(10)


externe_2017$Level <- as.factor(externe_2017$Level)

pal <- brewer.pal(n = 10, name = 'Paired')

vertex.col <- pal[(externe_2017$Level)]
#calculate degree
de=igraph::degree(graph_2017_ex)
plot(graph_2017_ex, vertex.label="", vertex.color=vertex.col, edge.color="slateblue", vertex.size=de*0.5, edge.width=E(graph_2017_ex)$weight*5)
legend("topleft",bty = "n",
       legend=levels((externe_2017$Level)),
       fill=pal, border=NA,cex=1)
```

```{r}
set.seed(10)

#graph - node size depends on betweeness centrality colored by levels


externe_2017$Level <- as.factor(externe_2017$Level)

pal <- brewer.pal(n = 10, name = 'Paired')

vertex.col <- pal[(externe_2017$Level)]

be=betweenness(graph_2017_ex, normalized=T)

plot(graph_2017_ex, vertex.label="", vertex.color=vertex.col, edge.color="slateblue", vertex.size=be*150)

legend("topleft",bty = "n",
       legend=levels((externe_2017$Level)),
       fill=pal, border=NA,cex=1)
```
```{r}
set.seed(10)


#graph - edge width depends onstrength centrality

externe_2017$Level <- as.factor(externe_2017$Level)

pal <- brewer.pal(n = 10, name = 'Paired')

vertex.col <- pal[(externe_2017$Level)]

st=graph.strength(graph_2017_ex)

plot(graph_2017_ex, vertex.label="", vertex.color=vertex.col, edge.color="slateblue", vertex.size=8,edge.width=st*0.3)

legend("topleft",bty = "n",
       legend=levels((externe_2017$Level)),
       fill=pal, border=NA)
```





```{r}
#Table for top 10 centrality
#sort dataframe by 10 highest degree
df_deg <- as.data.frame(de) %>% arrange(desc(as.data.frame(de)))
#add name column
df_deg$Name <- rownames(df_deg)
#rename rownames to empty
rownames(df_deg) <- c()
df_deg <- head(df_deg,10)
df_deg

```


```{r}
#merge degree dataframe to get institution and level

df_merged1<-merge(x = df_deg, y = externe_2017[, c("institutions", "Level","Name")], by = "Name", all.x=TRUE) 

head(df_merged1[!duplicated(df_merged1),])

```



```{r}
#Table for top 10 centrality
#sort dataframe by 10 highest degree
df_bet <- as.data.frame(be) %>% arrange(desc(as.data.frame(be)))
#add name column
df_bet$Name <- rownames(df_bet)
#rename rownames to empty
rownames(df_bet) <- c()
df_bet <- head(df_bet,10)
df_bet

```


```{r}
#merge degree dataframe to get institution and level

df_merged2<-merge(x = df_bet, y = externe_2017[, c("institutions", "Level","Name")], by = "Name", all.x=TRUE) 

head(df_merged2[!duplicated(df_merged2),])

```

## Sankey diagram and chord plot

```{r}
links <- data.frame(
source = c("Bachelor 2", "Bachelor 2", "Bachelor 2", "Exchange 1", "Bachelor 3", "Bachelor 3"),
target = c("Bachelor 3", "CY Tech", "Wild", "Bachelor 3", "Bachelor 4", "Exchange 2"),
value = c(12, 5, 1, 5, 13, 4)
)



nodes <- data.frame(name = c(as.character(links$source), as.character(links$target)) %>% unique())




links$ID.source <- match(links$source, nodes$name) - 1
links$ID.target <- match(links$target, nodes$name) - 1
```




```{r}
p <- sankeyNetwork(Links = links, Nodes = nodes, Source = "ID.source", Target = "ID.target", Value = "value", NodeID = "name", sinksRight = FALSE,fontSize = 15)



p
```


```{r}
temp_graph <- graph.data.frame(links)
adjaceny.matrix <- get.adjacency(temp_graph, sparse = FALSE, attr= "value")



chordDiagram(adjaceny.matrix, transparency = 0.75)
```











